### 2014-07-24 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
Spartanburg: Initial commit of plots for various tests

\section{Hose Flow Tests}

\subsection{DNXAXX}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A7}
\caption{Velocity at exterior Door A, Test HOSE\_DNXAXX}
\label{fig:HOSE_DNXAXX_BDP_A7}
\end{figure}

@@

\subsection{DNXOXF}

\begin{figure}[!ht]
\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A7}
\caption{Velocity at exterior Door A, Test HOSE\_DNXOXF}
\label{fig:HOSE_DNXOXF_BDP_A7}
\end{figure}

@@

\chapter{Appendix A}

>>>>

\section{286 College}

\subsection{Test 1, Living room fire with sprinkler}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_1_TC_A3}
\caption{286 College, Test 1, TC\_A3}
\label{fig:286_College_Test_1_TC_A3}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_1_TC_A4}
\caption{286 College, Test 1, TC\_A4}
\label{fig:286_College_Test_1_TC_A4}
\end{figure}

@@

\subsection{Test 2, Garage fire, exterior attack}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A1}
\caption{286 College, Test 2, TC\_A1}
\label{fig:286_College_Test_2_TC_A1}
\end{figure}

\subsection{Test 3, Living room fire}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_TC_A1}
\caption{286 College, Test 3, TC\_A1}
\label{fig:286_College_Test_3_TC_A1}
\end{figure}

\section{489 N. Forest}

\subsection{Test 1, Living room fire}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_A1}
\caption{489 N. Forest, Test 1, TC\_A1}
\label{fig:489_N_Forest_Test_1_TC_A1}
\end{figure}

\subsection{Test 2, Second floor bedroom fire}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A1}
\caption{489 N. Forest, Test 2, TC\_A1}
\label{fig:489_N_Forest_Test_2_TC_A1}
\end{figure}

\section{302 College}

\subsection{Test 1, Bedroom fire}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_A1}
\caption{302 College, Test 1, TC\_A1}
\label{fig:302_College_Test_1_TC_A1}
\end{figure}

\subsection{Test 2, Living room fire}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_A1}
\caption{302 College, Test 2, TC\_A1}
\label{fig:302_College_Test_2_TC_A1}
\end{figure}

\subsection{Test 3, Bathroom and attic fire}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A1}
\caption{302 College, Test 3, TC\_A1}
\label{fig:302_College_Test_3_TC_A1}
\end{figure}

\section{305 Manning}

\subsection{Test 1, Garage fire, interior attack}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A1}
\caption{305 Manning, Test 1, TC\_A1}
\label{fig:305_Manning_Test_1_TC_A1}
\end{figure}

\subsection{Test 2, Bedroom fire}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A1}
\caption{305 Manning, Test 2, TC\_A1}
\label{fig:305_Manning_Test_2_TC_A1}
\end{figure}

\subsection{Test 3, Complete burndown}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_3_TC_A1}
\caption{305 Manning, Test 3, TC\_A1}
\label{fig:305_Manning_Test_3_TC_A1}
\end{figure}

\section{289 Manning}

\subsection{Test 1, Basement fire}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A1}
\caption{286 College, Test 1, TC\_A1}
\label{fig:289_Manning_Test_1_TC_A1}
\end{figure}

\subsection{Test 2, Deck and attic fire}

\begin{figure}[!ht]
\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_2_TC_A1}
\caption{286 College, Test 2, TC\_A1}
\label{fig:289_Manning_Test_2_TC_A1}
\end{figure}

@@

\chapter{Placeholder}
